---
title: "RAND Request for 2019-2020 Administrative Data"
output: html_notebook
---

Each year RAND requests administrative data files from your community. By January 31, 2021, RAND is requesting delivery of the 2019-2020 academic year data files.

Please only send these files to RAND via Kiteworks (not email) to ensure appropriate handling of the sensitive information. Please respond to this email with the name of the individual(s) responsible for transmitting the data to RAND. That person(s) will receive the Kiteworks invitation email on Jan 24, 2021.

Responsible for creating data file: Stevens Dormezil

# Student Enrollment Charactertics

A student unique identifier is generated from the districts internal student id using the following methodology outlined in the wiki link below. This psuedo id is important for longitudinal data matching for the RAND team. All students enrolled at some point at any of the PSELI site schools are are included in this file.

<https://palmbeachschools.sharepoint.com/sites/ResearchandEvaluationWiki/SitePages/PsuedoID-Calculation.aspx>

The following is a list of the PSELI site schools. And overview of the PSELI project can be found in the wiki link below.


2751-Benoist Farms Elementary  
0601-Berkshire Elementary  
2731-Crosspointe Elementary - Annemarie Dilbert  
3261-Diamond View Elementary - Carolyn Seal  
2101-Egret Lake Community Elementary - Dionne Napier  
0621-Forest Hill Elementary - Scott McNichols  
1251-Glade View Elementary  
3351-Grassy Waters Elementary  
0631-Greenacres Elementary  
0012-Hope Centennial Elementary  
0751-Lantana Elementary - Janyn Robinson  
1101-Pahokee Elementary - Karen Abrams  
0781-Rolling Green Elementary  
0481-West Gate Elementary - Patricia Ordonez-Feliciano  

https://palmbeachschools.sharepoint.com/sites/ResearchandEvaluationWiki/SitePages/PSELI-School-Information.aspx

```{r, connection-setup}
library(DBI)
library(dbplyr)
library(tidyverse)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

con <- dbConnect(odbc::odbc(), "PBDW2")
```


```{r, connection-disconnect}
dbDisconnect(con)
```

